\texttt{JAXbind}: Easy bindings to JAX

### 2024-03-12 paper/paper.tex
paper.tex: Sync
paper.tex: Fix affiliation order
paper: unify adresses
paper.tex: \"u for ü
paper: intermix -> mix
paper: describe arguments of abstract funcs

        \author[1, 2, 3*]{Jakob Roth}
          \author[1*]{Martin Reinecke}
          \author[1, 2*]{Gordian Edenhofer}

      \affil[1]{Max Planck Institute for Astrophysics,
Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
      \affil[2]{Ludwig Maximilian University of Munich,
Geschwister-Scholl-Platz 1, 80539 Munich, Germany}
      \affil[3]{Technical University of Munich, Boltzmannstr. 3, 85748
Garching, Germany}
      \affil[*]{These authors contributed equally.}
  \date{\vspace{-7ex}}

@@

A plethora of high-performance code is not written in JAX and thus not
accessible from within JAX. Rewriting these is often infeasible and/or
inefficient. Ideally, we would like to intermix existing
high-performance code with JAX code. However, connecting code to JAX
requires knowledge of the internals of JAX and its C++ backend.

@@

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ jaxbind }

@@

To just-in-time compile the function, JAX needs to abstractly evaluate
the code, i.e.~it needs to be able to know the shape and dtype of the
output of the custom function given only the shape and dtype of the
input. We have to provide these abstract evaluation functions returning
the output shape and dtype given an input shape and dtype for \texttt{f}
as well as for the \texttt{vjp} application. The output shape of the
\texttt{jvp} is identical to the output shape of \texttt{f} itself and
does not need to be specified again.

>>>>

        \author[1, 2, 3*]{Jakob Roth}
          \author[1*]{Martin Reinecke}
          \author[1, 2, 4*]{Gordian Edenhofer}

      \affil[1]{Max Planck Institute for Astrophysics,
Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
      \affil[2]{Ludwig Maximilian University of Munich,
Geschwister-Scholl-Platz 1, 80539 Munich, Germany}
      \affil[3]{Technical University of Munich, Boltzmannstr. 3, 85748
Garching, Germany}
      \affil[4]{Department of Astrophysics, University of Vienna,
      T\"urkenschanzstr. 17, A-1180 Vienna, Austria}
      \affil[*]{These authors contributed equally.}
  \date{\vspace{-7ex}}

@@

A plethora of high-performance code is not written in JAX and thus not
accessible from within JAX. Rewriting these is often infeasible and/or
inefficient. Ideally, we would like to mix existing
high-performance code with JAX code. However, connecting code to JAX
requires knowledge of the internals of JAX and its C++ backend.

@@

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ jaxbind}

@@

To just-in-time compile the function, JAX needs to abstractly evaluate
the code, i.e.~it needs to be able to know the shape and dtype of the
output of the custom function given only the shape and dtype of the
input. We have to provide these abstract evaluation functions returning
the output shape and dtype given an input shape and dtype for \texttt{f}
as well as for the \texttt{vjp} application. The output shape of the
\texttt{jvp} is identical to the output shape of \texttt{f} itself and
does not need to be specified again.
The abstract evaluation functions take normal positional and keyword arguments.
